---
title: "intro_prisca"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro_prisca}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(prisca)
```

It gives an introduction to the package to do variance change point detection

We start simulating some data 

```{r}
T <- 500
x <- seq(0,1,1/(T-1))
y <- rep(0,T)
y[x<0.4] <- rnorm(sum(x<0.4),0,2)
y[x<0.1] <- rnorm(sum(x<0.1),0,1)
y[x>=0.4] <- rnorm(sum(x>=0.4),0,3)
y[x>=0.7] <- rnorm(sum(x>=0.7),0,0.6)
y[x>=0.85] <- rnorm(sum(x>=0.85),0,2)
plot(y)
```


We detect changes in variance using the prisca function. There a few basics parameters that we are required to set: a0 and L. See below if you don't want to select L


```{r}
a0<-0.00001
L <- 7
out <- prisca(y,L,a0)
```

We extract the credible sets, look at them, and plot them

```{r}
cs <- credible_set(out$alpha.mat,p=0.9)
cs
plot_prisca_sets(out)
```

I can also plot the data with the detected sets


```{r}
plot_prisca_data_sets(out)
```


If one does not want to choose L, there is an implementation of the autoprisca method described in the paper


```{r}
outAUTO <- autoprisca(y,a0,eps=0.01)
plot_prisca_sets(outAUTO)
```

